Inference for trans-dimensional Bayesian models with Diffusive Nested Sampling

### 2014-06-27 Documents/Paper/ms.tex
pgm figure in paper
Results figure
Got a title

\title{RJObject Paper}
\author{Brendon J. Brewer}

@@

@@

>>>>

\title{Inference for trans-dimensional Bayesian models with Diffusive Nested
Sampling}
\author{Brendon J. Brewer}

@@

\begin{figure}
\begin{center}
\includegraphics{pgm.pdf}
\caption{\it A probabilistic graphical model (PGM) depicting the kind
of model discussed in this paper. Produced using daft ({\tt daft-pgm.org}).
\label{fig:pgm}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{N_result.pdf}
\caption{The inference for $N$, the number of sinusoids, based on the
sinusoid data. The true value was $N=2$.
\label{fig:N_result}}
\end{center}
\end{figure}
